The K2 Halo Photometry Campaign

### 2019-04-05 paper/ms.tex
formatting

% describe saturation
The \kepler detector saturates at a magnitude of $K_p \sim 11.3$ in both long- (30~min) and short (1~min)-cadence data, as these both represent sums of 6~s exposures \citep{Gilliland2010}. Beyond this point, additional photons cause excess electrons to `bleed' into adjacent pixels in both directions along the column containing the bright star. This process occurs conservatively and simple aperture photometry (SAP) adding all the flux contained in a window around the bleed column has recovered light curves with precisions close to the photon noise limit of stars as bright as 16~Cyg~AB, $\theta$~Cyg and RR~Lyr \citep[e.g.][]{Kolenberg2011,2013MNRAS.433.1262W,Guzik2016}. In the nominal \kepler mission this was not attempted for all such bright stars, and in \ktwo, the several-pixel spacecraft motion significantly increased the size of the required apertures for SAP photometry of very saturated stars, while also making their systematics more difficult to deal with. While the second-version pixel-level-decorrelation (PLD) pipeline EVEREST~2.0 was able to correct systematics in saturated SAP photometry \citep{everest2}, this is rendered impossible for the very brightest stars whose bleed columns may run to the edge of the detector. Furthermore, bandwidth constraints meant that pixel data were not downloaded for many bright targets in \ktwo. It was therefore necessary to develop a method to recover good light curves from a smaller number of unsaturated pixels in a compact aperture around bright stars: halo photometry.

@@

% incorporation of k2sc
While the halo procedure produces in most cases a fairly clean light curve, there are nevertheless residual systematic errors related to spacecraft motion. In order to correct these, we employ the \textsc{k2sc} code \citep{Aigrain2015,k2sc}, which simultaneously models a light curve as a 3D Gaussian Process (GP) in time and predicted position (the K2 standard data product \textsc{pos\_corr}) in pixels $(x,y)$. The model prediction in time for fixed position is then a nonparametric model of the stellar variability, and the prediction in space evaluated for fixed time represents the pointing systematics and is subtracted from the input fluxes to obtain a final corrected flux, which is the time series we use and recommend for science. The target pixel files for C91, C92, and C101 include no position information, and there are no halo apertures for C112. As a result \textsc{k2sc}-corrected data are not available for these targets.

>>>>

% describe saturation
The \kepler detector saturates at a magnitude of $K_p \sim 11.3$ in both long- (30\,min) and short (1\,min)-cadence data, as these both represent sums of 6~s exposures \citep{Gilliland2010}. Beyond this point, additional photons cause excess electrons to `bleed' into adjacent pixels in both directions along the column containing the bright star. This process occurs conservatively and simple aperture photometry (SAP) adding all the flux contained in a window around the bleed column has recovered light curves with precisions close to the photon noise limit of stars as bright as 16~Cyg~AB, $\theta$~Cyg and RR~Lyr \citep[e.g.][]{Kolenberg2011,2013MNRAS.433.1262W,Guzik2016}. In the nominal \kepler mission this was not attempted for all such bright stars, and in \ktwo, the several-pixel spacecraft motion significantly increased the size of the required apertures for SAP photometry of very saturated stars, while also making their systematics more difficult to deal with. While the second-version pixel-level-decorrelation (PLD) pipeline EVEREST~2.0 was able to correct systematics in saturated SAP photometry \citep{everest2}, this is rendered impossible for the very brightest stars whose bleed columns may run to the edge of the detector. Furthermore, bandwidth constraints meant that pixel data were not downloaded for many bright targets in \ktwo. It was therefore necessary to develop a method to recover good light curves from a smaller number of unsaturated pixels in a compact aperture around bright stars: halo photometry.

@@

% incorporation of k2sc
While the halo procedure produces in most cases a fairly clean light curve, there are nevertheless residual systematic errors related to spacecraft motion. In order to correct these, we employ the \textsc{k2sc} code \citep{Aigrain2015,k2sc}, which simultaneously models a light curve as a 3D Gaussian Process (GP) in time and predicted position (the K2 standard data product \textsc{pos\_corr}) in pixels $(x,y)$. The model prediction in time for fixed position is then a nonparametric model of the stellar variability, and the prediction for the $x,y$ component evaluated for fixed time represents the pointing systematics. We subtract the systmatics model from the input fluxes to obtain a final corrected flux, which is the time series we use and recommend for science. The target pixel files for C91, C92, and C101 include no position information, and there are no halo apertures for C112. As a result \textsc{k2sc}-corrected data are not available for these targets.
